\section{RELEVANT EXPERIENCES}

{\customcventry
    {Toronto, Canada}
    {Fronix (\href{https://fronix.net}{Website}) — formerly IntractAI}
    {Technical Co-Founder}
    {Aug 2023 – Present (1 yr 6 mo)}{}{}}
    Co-founded startup pivoting from coding assistants to RL fine-tuning specialized reasoning models for enterprises.
    \begin{itemize}
        \item \textbf{Led reasoning R\&D} on Graph-RAG and fine-tuning techniques, improving code pass@1 by 20 pp.
        \item \textbf{Built scalable distributed stack} on 16×GPUs/2 nodes, cutting fine-tuning wall-time 2.1x.
        \item \textbf{Post-trained 3–70 B LLMs} with GRPO \& PPO for reasoning; +12 pp accuracy on internal evals.
        \item \textbf{Cut token latency 4x} via QLoRA quantization, vLLM, FlashAttention-2, fused KV-cache.
        % \item Built unit-test verifiers \& web agent, scraping 10 M code-commit pairs to fuel RLVR rewards.
        \item Accepted to Antler \& NextAI ($<$$3$-$5\%$ admit); interviewed by Y Combinator ($<$$7\%$ admit).
    \end{itemize}


{\customcventry
    {Remote, Canada \& US}
    {DeepR Analytics (Proprietary Trading Firm)}
    {Machine Learning Research Engineer}
    {Nov 2022 – Oct 2024 (2 yrs)}{}{}}
    Founding ML research engineer conducted research and built large-scale auto-trading pipeline and research tooling.
    \begin{itemize}
        \item \textbf{Built PyTorch pipeline that trained $>$1 M policy \& value nets}, adding \$35+ daily PnL/asset/share.
        \item \textbf{Implemented SOTA papers \& devised RL algorithms} in 10+ research projects; added \$20+ daily PnL/asset/share.
        \item \textbf{Migrated training/backtest stack to AWS ECS \& Fargate}, enabling on-demand scaling across 100+ assets.
        \item \textbf{Optimized data pipeline, simulated environments, eval pipeline}, async I/O; cut epoch time 9x and EC2 cost 4x.
        \item Raised test coverage to 85\% with Pytest; slashed prod bugs 45\% across ECS, CI, and C++ engine.
        % \item Automated hyper-parameter search (Optuna on Ray Tune); best configs lifted Sharpe ratio 22\%.
    \end{itemize}
  

{\customcventry{Edmonton, Canada}{University of Alberta (RLAI Lab)}{Research Associate}{Sep 2022 - Dec 2022 (4 months)}{}{}
}
\begin{itemize}
    \item \textbf{Redesigned ML codebase} for sensory data prediction, accelerating experimentation and analysis by \textbf{50\%} (\href{https://link.springer.com/article/10.1007/s10994-023-06413-x}{Publication}).
    \item \textbf{Developed and deployed optimized offline RL and control algorithms}, improving system performance by \textbf{21\%}.
\end{itemize}

{\customcventry{Edmonton, Canada}{Alberta Machine Intelligence Institute (Amii)}{Assistant AI Consultant}{Nov 2021 - Mar 2023 (1 year 5 months)}{}{}
}
% \begin{itemize}
% \item Consulting companies for \textbf{technical ML designs}:
% \begin{itemize}
%     \item ongoing technical coaching for teams
%     \item Helped a company in the gas and pipeline industry to potentially save \textbf{about \$10-15 million a year in costs} (\href{https://www.amii.ca/latest-from-amii/venturi-uses-machine-learning-reduce-emissions-increase-safety-pipelines/}{Blog Post})
% \end{itemize}

    
    % \item Contributed 50+ hours to the Startup Team as part of the program called SCALE AI: Supply Chain West
   % \item Assisted them in \textbf{consulting startups for coming up with better ML solutions}
% \end{itemize}
\begin{itemize}
    \item Provided continuous technical coaching to 5 enterprise teams, aligning projects with their business needs.
    \item Consulted an energy firm on problem formulation and ML design, \textbf{potentially saving \$10-15M annually} (\href{https://www.amii.ca/latest-from-amii/venturi-uses-machine-learning-reduce-emissions-increase-safety-pipelines/}{Blog}).
\end{itemize}

\customcventry{Remote/Edmonton, Canada}{Self-employed \textbf{(Leadership)}}{AI Mentor (\href{https://www.erfanmiahi.com/mentorship-program}{For More Info})}{Jan 2017 - present (7+ years)}{}{}
\begin{itemize}
    \item Mentoring \textbf{10+ students} (past and present) in AI research and engineering for \textbf{7+ years}.
    \item Mentored a University of Guilan (rank $1422$) student to secure a PhD at \textbf{Michigan State} University (rank $116$).
    % \item Designed a learning path for students who want to learn ML and Deep Learning 
    % \item Founded Rasht's inaugural artificial intelligence learning community, educating over 60 students (\href{https://github.com/rasht-school-of-ai/Meetup-Materials}{Teaching Materials})
\end{itemize}

\customcventry{Rasht, Iran}{Nilasoft}{Software Developer}{Nov 2015 – Nov 2017 (2+ years)}{}{}
\begin{itemize}
    \item \textbf{Built and optimized} a Spring/Angular e-commerce platform for \textbf{1K+ users} with \textbf{99.9\% uptime}.
\end{itemize}


% \customcventry{}{ICML 2022 and Neurips 2021}{Reviewer}{Remote}{}{}
% \begin{itemize}
%     \item Placed among the \textbf{top 10\% of reviewers} in ICML 2022
    % \item The purpose is to help the student understand what he wants and how to get it (\href{https://erfanmhi.github.io/pages/mentorship.html}{For More Info})
% \end{itemize}

    
%     % 		\customcvproject{}{}{
% 		  %      \textbf{at  - University of Guilan} \newline
%     %             I was educating students in the fields of Artificial Intelligence and Cognitive Science through lecturing, holding events, and mentorship. }
		
% %{School of AI, Rasht Chapter}
%             \vspace{1mm}
%     		{\customcventry{Oct 2018 -- present}{Rasht School of AI}{Dean}{Rasht, Iran}{}{}}
%     		\begin{itemize}
%     		    \item Established an artificial intelligence learning community in the city of Rasht for the first time
%     		    \item Organized five seminars and lectured in four of them (\href{https://github.com/rasht-school-of-ai/Meetup-Materials}{Slides})
%     		    \item Designed a learning path for students who want to learn ML and Deep Learning (\href{http://schoolofai.ir/learning-path/}{Our Website})
%     		    %such as Artificial Intelligence, Computational Neuroscience, Data Science, and Optimization algorithms.
%     		\end{itemize}


% {\customcventry{Oct 2016 – Nov 2017}{Nila Software Group}{Software Developer}{Rasht, Iran}{}{}
% }
% \begin{itemize}
%     \item Developed the server-client communication of a large-scale website following \textbf{software engineering best practices}
% \end{itemize}

% \customcventry{Aug 2018 -- Sep 2019}{Brain and Cognition Association \textbf{(Leading Experience)}}{Vice Chairman of the Modeling and Artificial Intelligence Committee}{Rasht, Iran}{}{}

% Web Developments\ & Django, Flask, Angular, HTML, CSS  \\
% Robotics\ & ROS, Robot Perception  \\
%Computer Vision\ & Pose Estimation, Object Detection, Face Recognition/Detection, etc \\



% \section{PROFESSIONAL RECOGNITION}
% \begin{itemize}
%     \item CCNA Routing \& Switching (Version 5.03) of CISCO (4 semester long course).
% \end{itemize}




